Mechanized Reasoning about a Capability Machine

### 2019-10-17 prisc-2020/paper.tex

\todo{Lars: the following is too hard to read and understand -- I suggest to omit it and just add a succinct description above}
\todo{begin}
Skorstensgaard et.
al.
use the World to define validity of capabilities, by relating the invariant of the region in question to certain standard islands for capabilities.

In the logical account, we use the capability points-to assertion to both describe what we may get from the read permission of a capability, and the restrictions imposed on us by the write permission of a capability. On the one hand, a points-to assertion lets us execute an instruction using that location. On the other, the permission of the points-to assertion restricts which updates are allowed, and thus which instructions will fail. The permission of the points-to assertion suffices to describe the behaviour of the above mentioned standard islands.

We want the value relation to give us the points-to predicate, while asserting that what the predicate points to is valid. The challenge is now to define how that should be done.
\todo{end}
% \subsection{Reasoning about Local State}
% \begin{itemize}
% 	\item How to reason about local state in high level languages
% 	\item public/private distinction
% 	\item TT style
% 	\item difficulties w/ iris invariants 
% \end{itemize}

>>>>

\todo{Lars: the following is too hard to read and understand -- I suggest to omit it and just add a succinct description above}
% \todo{begin}
% Skorstensgaard et.
% al.
% use the World to define validity of capabilities, by relating the invariant of the region in question to certain standard islands for capabilities.

% In the logical account, we use the capability points-to assertion to both describe what we may get from the read permission of a capability, and the restrictions imposed on us by the write permission of a capability. On the one hand, a points-to assertion lets us execute an instruction using that location. On the other, the permission of the points-to assertion restricts which updates are allowed, and thus which instructions will fail. The permission of the points-to assertion suffices to describe the behaviour of the above mentioned standard islands.

% We want the value relation to give us the points-to predicate, while asserting that what the predicate points to is valid. The challenge is now to define how that should be done.
% \todo{end}
% \subsection{Reasoning about Local State}
% \begin{itemize}
% 	\item How to reason about local state in high level languages
% 	\item public/private distinction
% 	\item TT style
% 	\item difficulties w/ iris invariants 
% \end{itemize}
